Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2022-01-21 Manuscript/FLPhish(Trans).tex
Phishing Mechanism-based Detection Bayesian Inference-based Reputation Mechanism 文字部分

\subsection{Phishing Mechanism-based Detection}
The proposed Ensemble FL still confronts the threat of Byzantine attacks. Malicious clients can manipulate their local model via label flipping. They mislabel the local dataset to build a `poisoned' local model. When malicious clients receive unlabeled data from the central server, they manufacture false predictions (called poisoned knowledge) and send these false predictions to the central server. Subsequently, the central server aggregates the false predictions as the labels of the unlabeled dataset. Then the central server trains the global model using these unlabeled datasets with the false aggregation predictions. Therefore, a flawed global model is produced. Inspired by the idea of ensemble learning, we consider utilizing the labeled data in the architecture of Ensemble FL to cope with Byzantine attacks. We called labeled data `bait'.
  \par Step-1: \ul{\textit{Local Model Training}} The ensemble of clients $C=\left \{ c_{1},c_{2},...,c_{n-1},c_{n} \right \}$. Each client $c_i$ possesses a local dataset $d_i$. At the beginning of the Ensemble FL, $c_{i}$ utilizes its local dataset $d_i$ to train a local model $\mathbf{m_i}$ as
  \begin{equation}
    \mathbf{m_i}=Train(d_i).
  \end{equation}
  \par Step-2: \ul{\textit{Dataset Transferring}} Central server $s$ selects $n$ samples of data $D_t$ from unlabeled dataset $D$ and $m$ samples of data $B_t$ from labeled dataset $B$ randomly. Then $s$ sends $D_t$ and $B_t$ to each client $c_i$ as
  \begin{equation}
    s \overset{{D_{t},B_{t}}}{\rightarrow} c_{i}.
  \end{equation}
  \par Step-3: \ul{\textit{Label Predicting}} Each client $c_i$ predicts the labels of the unlabeled data $D_t$ and the labeled data $B_t$:
  \begin{equation}
    \mathbf{k_i^t}=Predict(D_t, B_t, \mathbf{m_i})
  \end{equation}
  ($c_i$ can not distinguish between $D_t$ and $B_t$) via the local model trained by itself in Step 1  and sends its prediction back to the central server as the distilled knowledge $\mathbf{k_i^t}$:
  \begin{equation}
    \mathbf{k_i^t}=\begin{vmatrix}
      p_{1,1} & p_{1,2} & \cdots  & p_{1,g-1} & p_{1,g}\\ 
      \vdots  & \vdots & \ddots  & \vdots & \vdots\\ 
      p_{n,1} & p_{n,2} & \cdots  & p_{n,g-1} & p_{n,g}
      \end{vmatrix}.
  \end{equation}

@@

\subsection{Bayesian Inference-based Reputation Mechanism}
Server $s$ maintains a reputation list which records the reputation of all the clients $C$ in the model. Let $X_i$ be the reputation of the $c_i$ client which represents $s$'s belief that how likely client $c_i$ is a Byzantine client. The computation of $X_i$ is based on the accuracy $a_i^t$ of client $c_i$ from the 1st iteration to the $t$th iteration. Every time a new update of client $c_i$ comes to server $s$, $s$ uses the accuracy $a_i^t$ to update the value of $X_i$.
\par Initially, the reputation is neutral. Each client $c_i$ is taken as a benign client by server $s$ with a probability of 50\%. When a new update $\mathbf{k_i^t}$ comes to the server $s$, the reputation is updated by the $s$. When the reputation is lower than the threshold $r$, $s$ considers the client $c_i$ as a Byzantine client officially and discards the update coming from the client $c_i$. The updates of the client $c_i$ are reconsidered in the aggregation when the $X_i$ exceeds the threshold $r$.
\par We employ Bayesian inference to construct our reputation mechanism. Each data prediction made by client $c_i$ faces two situations: wrong predictions or correct predictions. Thus, the use of binomial parameter distributions becomes a natural choice for our reputation mechanism. Let $Y_i$ be the event that the number of wrong predictions and correct predictions made by client $c_i$ is $\alpha_i$ and $\beta_i$. Given $X_i=\gamma_i$, the conditional probability is 
\begin{equation}
    Pr(Y_i|X_i=\gamma _i)=\left ( \frac{\alpha _i+\beta _i}{\alpha _i} \right )\gamma {_{i}}^{\alpha_i}\left ( 1-\gamma_{i} \right )^{\beta_{i}}\label{equation_1}.
\end{equation}
where $\alpha_i$ and $\beta_i$ is the available evidence for the estimation of the $X$, and $\gamma_i$ is unknown. Eq. \ref{equation_1} indicates the likelihood function for $X$. According to Bayesian inference we compute the posterior probability as
\begin{equation}
    Pr(X_i=\gamma _i|Y_i)=\frac{Pr\left ( Y_{i}|X_{i}=\gamma_{i} \right )Pr(X_{i}=\gamma_{i})}{\int_{0}^{1}Pr\left ( Y_{i}|X_{i}=x \right )Pr(X_{i}=x)dx}\label{equation_2}.
\end{equation}
Given the posterior probability function, the final value for the expectation value of reputation $X$ is computed as
\begin{equation}
    E(X)=\int_{0}^{1}\frac{Pr\left ( Y_{i}|X_{i}=\gamma_{i} \right )Pr(X_{i}=\gamma_{i})}{\int_{0}^{1}Pr\left ( Y_{i}|X_{i}=x \right )Pr(X_{i}=x)dx}\gamma_{i}d\gamma_{i}\label{equation_3}.
\end{equation}
Furthermore, we decide to use the binomial parameter beta distribution to describe the distribution of X. Assume X is a random variable of the beta distribution with the parameters $(\alpha, \beta)$, the density function is
\begin{equation}
    f(x,\alpha,\beta)=\frac{1}{B(\alpha,\beta)}x^{\alpha-1}(1-x)^{\beta-1}\label{equation-4}.
\end{equation}
, where $B(\alpha, \beta)$ function is the beta function. Therefore we compute the expectation of $X$ as
\begin{equation}
    E(X)=\frac{\alpha}{\alpha+\beta}.
\end{equation}

>>>>

\subsection{Phishing Mechanism-based Detection}
Byzantine attacks are still a threat for the proposed Ensemble FL. Label flipping attacks allows malicious clients to modify their local model. They give the local dataset the incorrect labels in order to create a `poisoned' local model. When malevolent clients obtain unlabeled data from the central server, they create incorrect predictions (referred to as `poisoned knowledge') and submit them to the central server. The central server then aggregates the incorrect predictions as labels for the unlabeled dataset. The central server then uses these unlabeled datasets with the erroneous aggregation predictions to train the global model. As a result, a faulty global model is created. We suggest using labeled data in the design of Ensemble FL to cope with Byzantine attacks, inspired by the idea of ensemble learning. We called labeled data `bait'.
  \par Step-1: \ul{\textit{Local Model Training}} The ensemble of clients $C=\left \{ c_{1},c_{2},...,c_{n-1},c_{n} \right \}$. Each client $c_i$ possesses a local dataset $d_i$. At the beginning of the Ensemble FL, $c_{i}$ utilizes its local dataset $d_i$ to train a local model $\mathbf{m_i}$ as
  \begin{equation}
    \mathbf{m_i}=Train(d_i).
  \end{equation}
  \par Step-2: \ul{\textit{Dataset Transferring}} Central server $s$ selects $n$ samples of data $D_t$ from unlabeled dataset $D$ and $m$ samples of data $B_t$ from labeled dataset $B$ randomly. Then $s$ sends $D_t$ and $B_t$ to each client $c_i$ as
  \begin{equation}
    s \overset{{D_{t},B_{t}}}{\rightarrow} c_{i}.
  \end{equation}
  \par Step-3: \ul{\textit{Label Predicting}} Each client $c_i$ predicts the labels of the unlabeled data $D_t$ and the labeled data $B_t$:
  \begin{equation}
    \mathbf{k_i^t}=Predict(D_t, B_t, \mathbf{m_i})
  \end{equation}
  ($c_i$ can not distinguish between $D_t$ and $B_t$) via the local model trained by itself in Step 1  and sends its prediction back to the central server as the distilled knowledge $\mathbf{k_i^t}$:
  \begin{equation}
    \mathbf{k_i^t}=\begin{vmatrix}
      p_{1,1} & p_{1,2} & \cdots  & p_{1,g-1} & p_{1,g}\\ 
      \vdots  & \vdots & \ddots  & \vdots & \vdots\\ 
      p_{n,1} & p_{n,2} & \cdots  & p_{n,g-1} & p_{n,g}
      \end{vmatrix}.
  \end{equation}

@@

\subsection{Bayesian Inference-based Reputation Mechanism}
The server $s$ keeps track of the reputation of all the clients $C$ in the model in a reputation list. Let $X_i$ be the $c_i$ client's reputation, which represents $s$'s opinion of how probable client $c_i$ is to be a Byzantine client. The accuracy $a_i^t$ of client $c_i$ from the first iteration to the $t$th iteration is used to compute $X_i$. When client $c_i$ sends a new update to server $s$, $s$ uses the accuracy $a_i^t$ to update the value of $X_i$.
\par At first, the reputation is neutral. With a probability of 50\%, server $s$ considers each client $c_i$ to be a benign client. The reputation of the server $s$ is updated when a new update $\mathbf{k_i^t}$ arrives at the central server. When the client $c_i$'s reputation falls below the threshold $r$, $s$ considers the client $c_i$ to be a Byzantine client and discards the client's update. When the $X_i$ surpasses the threshold $r$, the client $c_i$ updates are reviewed in the aggregation.
\par We employ Bayesian inference to construct our reputation mechanism. Each data prediction made by client $c_i$ faces two situations: wrong predictions or correct predictions. Thus, the use of binomial parameter distributions becomes a natural choice for our reputation mechanism. Let $Y_i$ be the event that the number of wrong predictions and correct predictions made by client $c_i$ is $\alpha_i$ and $\beta_i$. Given $X_i=\gamma_i$, the conditional probability is 
\begin{equation}
    Pr(Y_i|X_i=\gamma _i)=\left ( \frac{\alpha _i+\beta _i}{\alpha _i} \right )\gamma {_{i}}^{\alpha_i}\left ( 1-\gamma_{i} \right )^{\beta_{i}}\label{equation_1}.
\end{equation}
where $\alpha_i$ and $\beta_i$ is the available evidence for the estimation of the $X$, and $\gamma_i$ is unknown. Eq. \ref{equation_1} indicates the likelihood function for $X$. According to Bayesian inference we compute the posterior probability as
\begin{equation}
    Pr(X_i=\gamma _i|Y_i)=\frac{Pr\left ( Y_{i}|X_{i}=\gamma_{i} \right )Pr(X_{i}=\gamma_{i})}{\int_{0}^{1}Pr\left ( Y_{i}|X_{i}=x \right )Pr(X_{i}=x)dx}\label{equation_2}.
\end{equation}
Given the posterior probability function, the final value for the expectation value of reputation $X$ is computed as
\begin{equation}
    E(X)=\int_{0}^{1}\frac{Pr\left ( Y_{i}|X_{i}=\gamma_{i} \right )Pr(X_{i}=\gamma_{i})}{\int_{0}^{1}Pr\left ( Y_{i}|X_{i}=x \right )Pr(X_{i}=x)dx}\gamma_{i}d\gamma_{i}\label{equation_3}.
\end{equation}
Furthermore, we decide to use the binomial parameter beta distribution to describe the distribution of X. Assume X is a random variable of the beta distribution with the parameters $(\alpha, \beta)$, the density function is
\begin{equation}
    f(x,\alpha,\beta)=\frac{1}{B(\alpha,\beta)}x^{\alpha-1}(1-x)^{\beta-1}\label{equation-4}.
\end{equation}
, where $B(\alpha, \beta)$ function is the beta function. Therefore we compute the expectation of $X$ as
\begin{equation}
    E(X)=\frac{\alpha}{\alpha+\beta}.
\end{equation}
